An Open-Source OpenSim Oculomotor Model for Kinematics and Dynamics Simulation

### 2018-07-16 doc/manuscript.tex
update results

The sign and magnitude of $\ddot{\theta}(t)$ both for the horizontal and
vertical displacement of the fixation target is used to actuate the
corresponding muscles in order to achieve the desired goal. \autoref{fig:model}
presents an instance of the model during simulation with the corresponding
muscles activated. \autoref{fig:simulated-saccade} depicts the simulated
coordinates, speeds and estimated \gls{em} activations that reproduce the
desired saccade trajectory.

>>>>

The sign and magnitude of $\ddot{\theta}(t)$ both for the horizontal and
vertical displacement of the fixation target is used to actuate the
corresponding muscles in order to achieve the desired goal. \autoref{fig:model}
presents an instance of the model during simulation with the corresponding
muscles activated. \autoref{fig:simulated-saccade} depicts the simulated
coordinates, speeds and estimated \gls{em} activations that reproduce the
desired saccade trajectory for different model parameters.
